\documentclass{article}
\usepackage[letterpaper, margin=1.0in]{geometry}

\begin{document}
\noindent
Robert Scanlon \\
CS 496 Fall 2017 \\
Final Project

\section*{Simple Pet Shelter API}
This API implements a system which can be used by a small animal shelter to
keep track of animals and volunteers. People and Pet entities can be
added, removed, and modified within the database. People can also be assigned to
act as `caretakers' for animals. Each animal in the database can have either 
zero or one caretaker. People can act as caretaker for zero or more animals.

\section*{People Objects}
People objects are returned with the following properties. \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Property}     & \textbf{Type}   & \textbf{Description} \\
	\hline
	id                    & String          & url safe identifier \\
	\hline
	self                  & Url String      & link to self (not an intrinsic property of People objects; \\
	                      &                 & added when request is made) \\
	\hline
	fname		      & String          & first name of person \\
	\hline
	lname	              & String          & last name of person \\
	\hline
	age	              & Integer         & age of person (years) \\
	\hline
	address               & String          & home address of person \\
	\hline
	pets	              & String[]        & a list containing the ids of pets for which this \\
	                      &                 & person is caretaker for \\
	\hline
\end{tabular}

\section*{Pet Objects}
Pet objects are returned with the following properties. \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Property}     & \textbf{Type}   & \textbf{Description} \\
	\hline
	id                    & String          & url safe identifier \\
	\hline
	self                  & Url String      & link to self (not an intrinsic property of Pet objects; \\
	                      &                 & added when request is made) \\
	\hline
	name		      & String          & name of pet \\
	\hline
	species               & String          & species of pet (cat, dog, etc.) \\
	\hline
	age                   & Integer	        & age of pet (years) \\
	\hline
	weight                & Integer         & weight of pet \\
	\hline
	caretaker             & String          & id of the person who is caretaker for this pet, \\
	                      &                 & NULL if the pet does not currently have a caretaker \\
	\hline
\end{tabular}

\section*{Get all People and Pets}
\texttt{GET /} \\
\textbf{Note:} Returns a json object containing "People" (a json list of all People in the
database) and "Pets" (a json list of all Pets in the database).

\section*{Get all People}
\texttt{GET /person} \\
\textbf{Note:} Returns a json list of all People in the database.

\section*{Get a single Person}
\texttt{GET /person/:id} \\
\textbf{Note:} A request containing a valid id string which does not
identify a Person in the database will return a 404 status code. A request
containing an invalid id string will return a status code 500 server error.

\section*{Get all Pets}
\texttt{GET /pet} \\
\textbf{Note:} Returns a json list of all Pets in the database.

\section*{Get single Pet}
\texttt{GET /pet/:id} \\
\textbf{Note:} A request containing a valid id string which does not
identify a Pet in the database will return a 404 status code. A request
containing an invalid id string will return a status code 500 server error.

\section*{Create a new Person}
\texttt{POST /person} \\
\textbf{Input} : application/json \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Name} & \textbf{Type} & \textbf{Description} \\
	\hline
	fname         & string        & \textbf{Required.} First name of Person \\
	\hline
	lname         & string        & \textbf{Required.} Last name of Person \\
	\hline
	age           & integer       & \textbf{Required.} Age of Person (years) \\
	\hline
	address       & integer       & \textbf{Required.} Address of Person \\
	\hline
\end{tabular} \\
\textbf{Note:} A request which contains invalid body data will return a
status code 400 Bad Request.

\section*{Create a new Pet}
\texttt{POST /pet} \\
\textbf{Input} : application/json \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Name} & \textbf{Type} & \textbf{Description} \\
	\hline
	name          & String        & \textbf{Required.} Name of pet \\
	\hline
	species       & String        & \textbf{Required.} Species of Pet \\
	\hline
	age           & integer       & \textbf{Required.} Age of Pet (years) \\
	\hline
	weight        & integer       & \textbf{Required.} Weight of Pet (lbs) \\
	\hline
\end{tabular} \\
\textbf{Note:} A request which contains invalid body data will return a
status code 400 Bad Request.

\section*{Modify a Person}
\texttt{PATCH /person/:id} \\
\textbf{Input} : application/json \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Name} & \textbf{Type} & \textbf{Description} \\
	\hline
	fname         & String        & New First Name of Person \\
	\hline
	lname         & String        & New Last Name of Person \\
	\hline
	age           & integer       & New age of Person (years) \\
	\hline
	address       & string        & New address of Person \\
	\hline
\end{tabular}
\\
Note: The \texttt{id}, and \texttt{Pets[]}
Person attributes cannot be modified through this request.

\section*{Modify a Pet}
\texttt{PATCH /pet/:id} \\
\textbf{Input} : application/json \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Name} & \textbf{Type} & \textbf{Description} \\
	\hline
	name          & String         & New Name of Pet \\
	\hline
	species       & String         & New Species of Pet \\
	\hline
	age           & integer        & New age of Pet (years) \\
	\hline
	weight        & integer        & New weight of Pet (lbs) \\
	\hline
\end{tabular}
\\
Note: The \texttt{id}, \texttt{caretaker} 
Pet attributes cannot be modified though this request.

\section*{Delete a Person}
\texttt{DELETE /person/:id} \\
Note: The caretaker attribute of all Pets for which this Person was caretaker for
is set to \texttt{NULL} upon the deletion of this Person.

\section*{Delete a Pet}
\texttt{DELETE /pet/:id} \\
Note: This Pet's id string is removed from a Person's pets[] attribute upon
deletion of this Pet, if said person was caretaker for this Pet.

\section*{Get All Pets With No Caretaker}
\texttt{GET /pet/free} \\
Note: This request will return a JSON array of all Pets in the database whose
\texttt{caretaker} attribute is \texttt{NULL}.

\section*{Add Care Relationship}
\texttt{PUT /pet/:id/caretaker} \\
\textbf{Input} : application/json \\
\begin{tabular}{| l | l | l |}
	\hline
	\textbf{Name} & \textbf{Type} & \textbf{Description} \\
	\hline
	person\_id   & string         & \textbf{Required.} Person id string of the Person \\
		     &                & who will be caretaker for this Pet. \\
	\hline
\end{tabular} \\
Note: If the Pet identified by the \texttt{id} in the url already has a caretaker,
the \texttt{id} in the url does not match a Pet in the database, or the \texttt{id}
passed in the request body does not match a person in the database, a \texttt{400} error code
is returned along with an appropriate error message. If the request is successful the Pet's
\texttt{caretaker} is updated, along with the Person's \texttt{pets} list.

\section*{Remove Care Relationship}
\texttt{PATCH /pet/:id/caretaker} \\
Note: If the \texttt{id} passed in the url does not identify a Pet in the database,
or the person \texttt{id} of this Pets \texttt{caretaker} does not identify a Person
in the database, a \texttt{400} error is returned with the appropriate message.
If the request is successful, the Pet's \texttt{caretaker} attribute is set to
\texttt{NULL} and the Pet's \texttt{id} string is removed from the Person's
\texttt{pets} list.

\section*{Get a Person's Pets}
\texttt{GET /person/:id/pets} \\
Note: Returns a list of Pets who this person is caretaker for. If the \texttt{id}
does not identify a Person in the database, a 404 error is returned.

\end{document}
